### 2014-09-25 LaTeX/RhodiumTheory.tex
minor comments

@@

@@

That armed conflict near and within cities should impact national economic performance is not surprising given the existing body of literature that suggests a close relationship between urban agglomeration and national economies. \cite[p. 137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the nation state in economic analysis \citep{jacobs:1969,jacobs:1984}.  In the past three decades, economists have followed Jacobs' lead and investigated city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999}.

>>>>

% I like the last idea where we say that conflict impedes trade between cities.

@@

% Do we even need to bring up Imai and Weinstein here? I dont think it helps us if people keep contrasting our approach with theirs as they read our paper.

@@

That armed conflict near and within cities should impact national economic performance is not surprising given the existing body of literature that suggests a close relationship between urban agglomeration and national economies. \cite[p. 137]{quigley:1998} concludes that ``large cities have been and will continue to be an important source of economic growth.''  This echoes the work of Jane Jacobs who argued that cities are the primary motivators of state economies and should be given primacy over the nation state in economic analysis \citep{jacobs:1969,jacobs:1984}.  In the past three decades, economists have followed Jacobs' lead and investigated city-level economic drivers \citep{lucas:1988, ciccone:hall:1996, begg:1999}. One oft-cited mechanism by which cities can provide economic advantages to industry is knowledge spillover. Industries that concentrate in cities benefit from one another through knowledge transfer \citep{jaffe:etal:1993, glaeser:1994, firestone:2010}.  Empirical estimates of agglomeration effects indicate that a doubling of employment density correspond to a 5\% increase in labor productivity \citep{ciccone:hall:1996,ciccone:2002}.

% Add some references here about cities accounting for larger portions of economies. Would be nice if we found this to be particularly true for developing countries as well.
